\section{Convolutional Neural Networks}

\begin{itemize}[wide, labelwidth=!, labelindent=0pt]
\itemsep0em 
    \item Parameter sharing: A feature detector (such as a vertical edge detector) that’s useful in one part of the image is probably useful in another part of the image.
    \item Sparsity of connections: In each layer, each output value depends only on a small number of inputs. \vspace*{-\baselineskip}
\end{itemize}

\textbf{Padding:} Can be valid or same. Valid means no padding. Same means output will have same $n$ as input. To accomplish this, we choose $p = \frac{f-1}{2}$.

\textbf{Dimensions:}

$f^{[l]} = $ filter size

$p^{[l]} = $ padding

$s^{[l]} = $ stride

$n_C^{[l]} = $ number of filters

Each filter is: $f^{[l]} \times f^{[l]} \times n_C^{[l-1]}$

Activations are: $a^{[l]} = n_H^{[l]} \times n_W^{[l]} \times n_C^{[l]}$

or: $A^{[l]} = m \times n_H^{[l]} \times n_W^{[l]} \times n_C^{[l]}$

Weights are: $f^{[l]} \times f^{[l]} \times n_C^{[l-1]} \times n_C^{[l]}$

Biases are: $n_C^{[l]}$

Input is: $n_H^{[l-1]} \times n_W^{[l-1]} \times n_C^{[l-1]}$

Output is: $n_H^{[l]} \times n_W^{[l]} \times n_C^{[l]}$

$n_H^{[l]} = \lfloor \frac{n_H^{[l-1]} + 2p^{[l]} - f^{[l]}}{s^{[l]}} + 1 \rfloor$

num_params $= (f^{[l]} * f^{[l]} * n_C^{[l-1]} + 1) * n_C^{[l]}$

\textbf{1 $\times$ 1 Convolutions: } Allow you to shrink or expand the number of channels in an image (like pooling does for $n_W$ and $n_H$). Takes element-wise product of a pixel's channel. Sometimes called a network in network. Can be used as a bottleneck to reduce number of multiplication operations.

\textbf{Inception Network: } Allows you to apply many different types of filters instead of trying to choose between them. Must use same padding for convolutions.

\textbf{Resideual Networks:}

Skips over layers and adds in activation from first layer in block to $z$ of last layer in block. Adding layers to a ResNet doesn't hurt because it is easy for residual blocks to learn the identity function, and it still gives them the chance to learn a more complex function if it will boost performance. Assumes $a^{[l+2]}$ and $a^{[l]}$ have the same dimension, so it's common to use same padding on convolutions, but if not you can add $W_s$ to change the shape of $a^{[l]}$. Here $a^{[l+2]} = g(z^{[l+2]} + a^{[l]})$.



